Title Goes Here

### 2019-03-25 analysis/paper/paper.Rmd
some updates for plots

>>>>

```{r get-data, eval = FALSE}
# summarise the ornaments by layers
library(tidyverse)
library(ggplot2)

# L5 and L6 represent pre-European contact period, 
# L4 was the time of European contact, and 
# L2 and L1 was the period of Chinese contact.

ornaments_period <- 
kwl_upper %>% 
  filter(!is.na(`6-layers`)) %>% 
  mutate(period = case_when(
    `6-layers` %in% 1:2 ~ "Chinese Contact",
    `6-layers` == 4 ~ "European Contact",
    `6-layers` %in% 5:6 ~ "Before European Contact",
     TRUE ~ "other"
  )) %>% 
  filter(period != "other")

# need to reorder, try https://forcats.tidyverse.org/reference/index.html
# reorder factor for categories (by frequency) and period (manually)
# total number of ornaments for each categories 
ornaments_count_test <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  group_by(Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

ggplot(ornaments_count_test,
       aes(Categories, n)) +
  geom_col() +
  coord_flip() +
  labs(y = "Frequency",
       x = "Categories") +
  theme_minimal(base_size = 14)

# categories of ornaments by period
ornaments_count <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  group_by(period, Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

ggplot(transform(ornaments_count,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Categories, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Categories") +
  theme_minimal(base_size = 14)
```

```{r get-data, eval = FALSE}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition == 'complete',
         Categories == 'Golden bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

ggplot(transform(ornaments_intact_gold,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Perforation_average)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Golden beads") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

# plot for intact agate bead by period
ornaments_intact_agate <-
  ornaments_period %>% 
  filter(Condition == c('complete','near-complete'),
         Categories == 'Agate bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

ggplot(ornaments_intact_agate, 
       aes(Length, Width, col = period))+
  geom_point() +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Agate beads") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))
```
